\chapter{Zeros}
\label{ch:zeros}

We recall a rather explicit connection between the moduli of the zeros of an analytic function and the modulus of the function itself:

\begin{theorem}[Jensen]
    Let $f$ be analytic on $B(0, R)$ with $f(0) \neq 0$ and let $(r_j)_{j=1}^n$ denote the moduli of the zeros of $f$ in $B(0, R)$ arranged in a non-decreasing sequence. Then, for $r_m < r < r_{m+1}$, we have
    $$ \frac{1}{2 \pi} \int_0^{2\pi} \log \vert f(r e^{i \vartheta}) \vert \diff \vartheta = \log \vert f(0) \vert + \log \frac{r^n}{r_1 \hdots r_m}. $$
\end{theorem}

\begin{definition}
    Let $f$ be analytic on $B(0, R)$. Then for $0 < r < R$ we denote by $n_f(r)$ the number of zeros of $f$ in $\cl{B(0,r)}$.
\end{definition}

\begin{corollary}
    Let $f$ be analytic on $B(0, R)$ with $f(0) \neq 0$. Then for $0 < r < R$ we have
    $$ \frac{1}{2 \pi} \int_0^{2\pi} \log \vert f(re^{i \vartheta}) \vert \diff \vartheta = \log \vert f(0) \vert + \int_0^r \frac{n_f(s)}{s} \diff s $$
\end{corollary}

\begin{proof}
    \todo{TODO.}
\end{proof}

In particular, we observe that the more zeros a function $f(z)$ has, the faster its modulus must grow as $\vert z \vert \to \infty$. The converse is naturally false, as seen by iterated exponentials.

\begin{definition}
    Let $f$ be an entire function satisfying $f(0) \neq 0$. Let $(r_j)_{j \in \N}$ denote the moduli of the zeros of $f$ (if any) arranged in non-decreasing order. Then
    $$ \lambda_f \coloneqq \inf \left\{ \lambda > 0 : \sum_{n=1}^\infty \frac{1}{r^\lambda_n} < \infty \right\} $$
    is called the \emph{exponent of convergence of the zeros of f}. If $f$ has finitely many zeros, then we set $\lambda_f = 0$ by convention. \todo{I am not sure about this -- the paper only establishes this convention if $f$ has no zeros at all.}

    Furthermore, the \emph{exponent of convergence of the $a$-points of $f$} is defined as exponent of convergence of $f(z) - a$.
\end{definition}

\begin{theorem} \label{thm:inequality-order-exponent-of-convergence}
    Let $f$ be an entire function of finite order. Then $\lambda_f \leq \rho_f$.
\end{theorem}

\begin{proof}
    \todo{TODO.}
\end{proof}

\begin{example} \label{exm:exponent-of-convergence}
    \todo{An example of a series where we see some convergence for some appropriate function using the above.}
\end{example}

\begin{theorem} \label{thm:exponent-of-convergence-weierstrass-product}
    Let $E$ be a Weierstrass canonical product of finite order. Then $\lambda_E = \rho_E$.
\end{theorem}

\begin{proof}
    \todo{TODO.}
\end{proof}

\begin{theorem} \label{thm:finite-non-integer-order-equals-exponent-of-convergence}
    Let $f$ be an entire function of finite, non-integer order. Then $\rho_f = \lambda_f$.
\end{theorem}

\begin{proof}
    By \Cref{thm:inequality-order-exponent-of-convergence} we have $\lambda_f \leq \rho_f$. Invoking Hadamard's Theorem we can write $f = e^Q E$ for a polynomial $Q$ with $\deg Q \leq \rho_f$. Since $\rho_f$ is not an integer, this implies $\deg Q \leq \lfloor \rho_f \rfloor < \rho_f$. Now, again by Hadamard's Theorem, $e^Q$ has order $\deg Q$ and by \Cref{thm:exponent-of-convergence-weierstrass-product} $E$ has order $\lambda_f$. Using \Cref{prop:algebraic-properties-order} we obtain
    $$ \rho_f \leq \max \{ \deg Q, \lambda_f \} = \lambda_f \leq \rho_f, $$
    implying $\rho_f = \lambda_f$.
\end{proof}

\begin{theorem} \label{thm:finite-non-integer-order-infinite-zeros}
    Let $f$ be an entire function of finite, non-integer order. Then $f$ has infinitely many zeros.
\end{theorem}

\begin{proof}
    By \Cref{thm:finite-non-integer-order-equals-exponent-of-convergence} we have $\rho_f = \lambda_f$. Since $\rho_f$ is not an integer, $\lambda_f > 0$, which implies that $f$ has infinitely many zeros.
\end{proof}

\todo{Maybe introduce Borel exceptional values as a definition? But then again, I will never need them again. Maybe also add a remark on the relation to lacunary values (Picard).}

\begin{theorem}[Borel] \label{thm:existence-borel-exceptional-values}
    \todo{Existence of Borel exceptional values.}
\end{theorem}

\begin{proof}
    \todo{TODO.}
\end{proof}