\chapter{Picard's Great Theorem}
\label{ch:picards-great-theorem}

An isolated singularity of a holomorphic function which is not removable nor a pole, is called an \emph{essential singularity}. While holomorphic functions are fairly well-behaved near their removable singularities and poles, the same cannot be said for their essential singularities.

An interesting result is already given by the Casorati--Weierstraß Theorem: Let $G \subseteq \C$ be open, $w \in G$ and suppose $f \in H(G \setminus \{ w \})$ such that $f$ has an essential singularity at $w$. Then, for any punctured neighborhood $U \subseteq G \setminus \{ w \}$ of $w$, the set $f(U)$ is dense in $\C$.

Picard's Great Theorem will show that $f(U)$ is not only dense in $\C$, but there is at most one value which is not taken on by $f$ infinitely often on any such punctured neighborhood.

We will reach the proof the same way as in Remmert \cite{remmert-function-theory}. We first study Bloch's Theorem, which estimates the size of disks in the image of a holomorphic map. As a corollary of the proof we obtain Picard's Little Theorem, which states that a non-constant entire function omits at most one value.

One can see this as a motivation to intently study (non-entire) holomorphic functions that omit (at least) two values. For such functions, Schottky's Theorem will give an upper bound on their modulus. We use this to obtain the Fundamental Normality Test, which asserts normality of any family of holomorphic functions omitting two fixed values.

Restricting the domain in the above to be the punctured unit disk, we obtain that such functions cannot have an essential singularity at the origin, which will imply Picard's Great Theorem.

\input{chapters/picards-great-theorem/bloch.tex}
\input{chapters/picards-great-theorem/schottky.tex}
\input{chapters/picards-great-theorem/normal-families.tex}
\input{chapters/picards-great-theorem/picard.tex}